Metropolitan Areas (Deaths & Case)

### 2020-11-11 KPMG Team/Dashboard/msa_areas_map.Rmd

# --------------------------------------# 
# without filtering (run this)
census_msa <- census_msa_merge
# ------------------------------------ #

@@

# Rank of MSAs according to total cases
head(msa_covid_sum, 10)

@@

# ---- To Find MSA codes ---- #
# head(msa_covid_sum, 10)

@@

>>>>

# --------------------------------------# 
# without filtering (run this)
census_msa <- census_msa_merge
# ------------------------------------ #
names(nyt)

county_sum <- nyt %>% 
  group_by(county, state, fips) %>%
  summarise(cases_sum = sum(cases, na.rm = TRUE))

@@

# Rank of MSAs according to total cases
head(msa_covid_sum, 50)

@@

# ---- To Find MSA codes ---- #

# head(msa_covid_sum, 10)

@@

# Plot State Map with Metro Areas

# mapping packages needed 
library(leaflet)
library(maptools)
library(rgdal)

# interactive visualization
library(plotly)

library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

library(tigris)
library(usmap) # to get US Map Data

library(jsonlite) # from FIPS -> Geo (lat, long)

# states in Texas 
plot_usmap(include = .midwest_region, labels = TRUE)

# get FIPS codes (state + county)
# fips(state = "CA", county = "Orange")

# FIPS county codes to Lat Long
geoFips <- function() {

# get lat long data from US Census 
# https://www.census.gov/geographies/mapping-files/time-series/geo/carto-boundary-file.html
county_lines <- st_read("county_shape/cb_2018_us_county_500k.shp")

# add FIPS as a variable from State Fips and County Fips
county_lines <- county_lines %>% 
  mutate(fips = paste(STATEFP, COUNTYFP, sep = ""))

# add lat long attributes to county dataset          
county_geo <- merge(county_lines, county_sum, by = "fips")
county_map <- county_geo %>% st_transform('+proj=longlat +datum=WGS84')

outside_mainland <- c("02", "15", "72", "2", "3")
islands <- c("Virgin Islands", "Northern Mariana Islands")

county_map_US <- county_map %>% 
  filter(!STATEFP %in% outside_mainland) %>% 
  filter(!state %in% islands) # remove alaska and hawaii

ggplot(data = county_map_US) +
  geom_sf(aes(fill = cases_sum)) + 
  scale_fill_viridis_c(option = "magma", direction = 1)

county_map_NY <- county_map %>% 
  filter(STATEFP == 36) # remove alaska and hawaii

ggplot(data = county_map_NY) +
  geom_sf(aes(fill = cases_sum)) + 
  scale_fill_viridis_c(option = "magma", direction = -1)

names(county_map_US)

fips(state = "New York")

table(c(county_map_US$statefp, county_map_US$state))

# PLOT FUNCTION 
# county state map 
county_state_map <- function(state_name) {

  fips_code <- fips(state = state_name)

  county_map_state <- county_map %>% 
  filter(STATEFP == fips_code)

  ggplot(data = county_map_state) +
  geom_sf(aes(fill = cases_sum)) + 
  scale_fill_viridis_c(option = "magma", direction = -1)

W <- county_state_map("Wisconsin")
